Analyzing Toronto's homeless population trends

### 2024-04-19 paper/paper.qmd
paper

---
title: "Analyzing the Influence of Gender and Age on Shelter Return numbers in Toronto In 2023"
author: 
  - Xuecheng Gao
thanks: "https://github.com/XuechengGao/Shelter_Return_numbers_in_Toronto_2023.git"
date: today
date-format: long
abstract: "Homelessness is an issue that many cities are currently facing. This study investigates data on people in Toronto shelters from 2020 to 2023. We analyzed the data recorded at shelters using negative binomials to examine the relationship between population groups and shelter intake data. Significant correlations were found between gender, age demographics, and shelter returns. These data analyses provide additional reference data for Toronto when addressing homelessness."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analyzing Toronto's homeless population trends"
author: 
  - Xuecheng Gao
thanks: "https://github.com/XuechengGao/Shelter_Return_numbers_in_Toronto_2023.git"
date: today
date-format: long
abstract: "Homelessness is an issue that many cities are currently facing. This study investigates data on people in Toronto shelters from 2020 to 2023. We analyzed the data recorded at shelters using negative binomials to examine the relationship between population groups and shelter intake data. Significant correlations were found between gender, age demographics, and shelter returns. These data analyses provide additional reference data for Toronto when addressing homelessness."
format: pdf
number-sections: true
bibliography: references.bib
---
